\subsection{Results}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Camera mount design}

\begin{itemize}
	\item Requirements definition.
	\item CAD part and drawing design. See figures \ref{fig_cammountp1}, \ref{fig_cammountp2} and \ref{fig_cammountp3} at the Appendix.
	\item Research on the camera's positioning for propper stere visions.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Edge detection research}

\begin{itemize}
	\item Knowledge about gaussian, sobel and canny theory used for edge detection.
	\item Possible optimizations to and limitations of the code were identified.
	\item Hint about GPU usage.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{General-purpose computing on graphics processing units}

\begin{itemize}
	\item Knowledge about Pi's GPU.
	\item Pointers to GPU based solutions for the application.
	\item Study of OpenGLSL was started but not finished.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{STM32 - IDE installation}

\begin{itemize}
	\item IAR Embedded Workbench ARM v7.10 was chosen and installed.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{STM32 - SPI and DMA}
\begin{itemize}
	\item Successful communication test in slave mode (using DMA) with the Raspberry Pi.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Raspberry Pi - SPI}

\begin{itemize}
	\item Low level library installed. This allows using SPI directly commanding the processor (skipping the Linux kernel).
	\item Successful communication test in master mode with the STM32 as slave.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Raspberry Pi - Performance improvements}

\begin{itemize}
	\item A prioritized list (for the application at hand) of potential optimizations to have in mind:
	\begin{itemize}
		\item Using the GPU for image processing.
		\item Overclocking.
		\item Shutdown unused modules.
		\item Running the raspberry "bare bones", without Linux.
	\end{itemize}
\end{itemize}
