\subsection{Administrative Process}

There were some pending administrative procedures that are reported here as a reference and information for future UDEM students that could participate in a similar program. Upon my arrival to the laboratory I was taken to Jennyfer DUBERVILLE to check for pending steps at the administrative procedures. The documents that were sent via Internet were checked for possible corrections. These documents are:
\begin{itemize}
	\item Student card.
	\item Copy of the last diploma (mine was from high school).
	\item Copy of my passport.
	\item The contract/agreement (signed by me and the Dean of UDEM's DIT)
\end{itemize}
After reviewing the documents a form was given to my assessor and the rules/regulations (mostly about the use of laboratory's resources such as internet, computers, etcetera) were given to me. I signed of agreement to the rules and declaring the date of arrival to the laboratory. I was reminded I have to pay the "social security" and "civil liability" fees when prompted. I was also informed that for receiving the gratification I have to open a bank account in a French bank and I was told I was going to be contacted with a person that could help me with that.

Finally I was given my authentication credentials which I will be using to connect to the wireless network and to sign in to my computer. My assigned computer was installed and some other restrictions were informed (you can not connect to the wired network, you can not install software other than from Debian's repositories, how to access the schools backed up servers, etcetera).
